---
title: "NaiveBayes"
author: "Dar Nettler & Carmela Davidovsky"
date: "27 áðåáîáø 2017"
output: html_document
---
# Classification Using Naive bayes

### Libraries used in this algorithm:
```{r}
#install.packages("tidyr")
library(tidyr)
#install.packages("ggplot2")
library(ggplot2)
#install.packages('e1071')
library(e1071)
```

### Read dataframe:

```{r}
df<-read.csv("train.csv",na.strings = "")
```


### Turn Survived and Pclass into factor:

```{r}
df$Survived<- as.factor(df$Survived)
df$Pclass<- as.factor(df$Pclass)
```

### Delete the passengerId, Ticket and name columns from the data frame and fill missing values of age with mean:

```{r}
df <- subset(df,select = -c(PassengerId,Ticket,Name))
```

### Visualization of the behavior of each feature vs. the target feature (surviving or not).

It is easier to explore factors and numeric features separately. Here we divide the features' names to numerics and factors:

```{r}
cols<- 1:dim(df)[2]
factors <- cols[sapply(df,is.factor)]
numerics <- cols[!sapply(df,is.factor)]
```

We now tide the data two times: the first is for categorial data and the second for numeric data.

```{r}
df_tidy_factors<-gather(df[,factors],"feature","value",-1)
df_tidy_numerics<-gather(cbind(Survived=df[,1],df[,numerics]),"feature","value",-1)

```

The first plot describes only categorical features (factors):

```{r}
qplot(x=value,data=df_tidy_factors,fill=Survived) + facet_grid(~feature,scales="free")
```

One more plot for numeric features:

```{r}
qplot(x=value,data=df_tidy_numerics,fill=Survived) + facet_grid(~feature,scales="free")
```

### Seperate the dataframe into train and test:

```{r}
set.seed(123)
indices <- sample(1:nrow(df),nrow(df)*0.87)
train<- df[indices,]
test<- df[-indices,]
```

### Train a naive bayes model:

```{r}
nb_model <- naiveBayes(Survived~.,data = train)
pred <- predict(nb_model,test)
```

The accuracy of the model:

```{r}
mean(pred==test$Survived)
```

### Load the test dataframe: 

```{r}
new_df <-read.csv('test.csv',na.strings = "")
```

### Save the passengerIds:

```{r}
ids<- new_df$PassengerId
```

### Turn Survived to a factor and delete the same columns we deleted in the train set:

```{r}
new_df$Pclass<- as.factor(new_df$Pclass)
new_df <- subset(new_df,select = -c(PassengerId,Ticket,Name))
```

### Predict the rows in the test set with the naive bayes model:

```{r}
new_pred<- predict(nb_model,new_df,na.action = na.pass)
```

### Write the predictions into file:

```{r}
res <- cbind(PassengerId=ids,Survived=as.character(new_pred))
write.csv(res,file="NaiveBayes.csv",row.names = F)

```
