---
title: "Ensemble"
author: "Dar Nettler & Carmela Davidovsky"
date: "28 áðåáîáø 2017"
output: html_document
---
# Classification Using Ensemble of rpart and GBM

### Libraries used in this algorithm:
```{r}
#install.packages("caretEnsemble")
library(caretEnsemble)
#install("caret")
library(caret)

```

### Read dataframe:

```{r}
df<-read.csv("train.csv",na.strings = "")
```

### Turn Survived and Pclass into factor:

```{r}
df$Survived<- as.factor(df$Survived)
df$Pclass<- as.factor(df$Pclass)
```

### Delete the passengerId, Ticket, Cabin and name columns from the data frame and fill missing values of age with mean, and missing values of embarked with 'S'.

```{r}
df <- subset(df,select = -c(PassengerId,Ticket,Name,Cabin))
df[is.na(df[,"Age"]),"Age"]<-mean(df[,"Age"],na.rm = TRUE)
df$Embarked[is.na(df$Embarked)]<-'S'
```

### Defining the Ensemble's Members:
We start by running several models together, with the *caretList* method. These models will be compared, and if they'll suit the job, we'll compose an ensemble out of theme.
```{r}
set.seed(123)
models <- caretList(
  make.names(Survived) ~ .,
  data = df,metric="Accuracy",
    trControl = 
  trainControl(
    method = "cv",
    number = 10,
    savePredictions = 'final',
    classProbs=TRUE
  ),
  tuneList = list(
    gbm=caretModelSpec(
      method="gbm", verbose=FALSE,
      tuneGrid=data.frame(
        .n.trees=c(5),
        .interaction.depth=6,
        .shrinkage=c(0.1,0.3,0.5),
        .n.minobsinnode=5)
      ),
    rpart=caretModelSpec(method = "rpart")
  )
)

```

### check the results and check if there's a correlation between the models:

```{r}
results <- resamples(models)
dotplot(results)
splom(results)
modelCor(results)
```

### Stack using random forest:

```{r}
set.seed(123)
stack.rf <- caretStack(
  models,
  method = "rf",
  metric = "Accuracy",
  trControl = trainControl(method="cv",
    number = 10,
    summaryFunction = twoClassSummary,
    classProbs = TRUE
  )
)
```

### Load the test dataframe and add a empty column of the class (the model and the test set must be the same size): 

```{r}
new_df <-read.csv('test.csv',na.strings = "")
new_df$Survived<-NA
```

### Save the passengerIds:

```{r}
ids<- new_df$PassengerId
```

### Turn Survived to a factor and delete the same columns we deleted in the train set. fill missing values in age and fare with the mean of the column:

```{r}
new_df$Pclass<- as.factor(new_df$Pclass)
new_df <- subset(new_df,select = -c(PassengerId,Ticket,Name,Cabin))
new_df[is.na(new_df[,"Age"]),"Age"]<-mean(new_df[,"Age"],na.rm = TRUE)
new_df[is.na(new_df[,"Fare"]),"Fare"]<-mean(new_df[,"Fare"],na.rm = TRUE)
```

### Predict the rows in the test set with the ensemble model and turn the levels into *0* and *1*:

```{r}
new_pred<-predict(stack.rf, newdata=new_df)
levels(new_pred)<-c("0","1")
```

### Write the predictions into file:

```{r}
res <- cbind(PassengerId=ids,Survived=as.character(new_pred))

write.csv(res,file="Ensemble results.csv",row.names = F)

```
