---
title: "GBM"
author: "Dar Nettler & Carmela Davidovsky"
date: "27 áðåáîáø 2017"
output: html_document
---

# Classification Using GBM with caret

### Libraries used in this algorithm:

```{r}
#install.packages("gbm")
library(gbm)
#install.packages("caret")
library(caret)
```

### Read dataframe:

```{r}
df<-read.csv("train.csv",na.strings = "")
```

### Turn Survived and Pclass into factor:

```{r}
df$Survived<- as.factor(df$Survived)
df$Pclass<- as.factor(df$Pclass)
```

### Delete the passengerId, Ticket and name columns from the data frame and fill missing values of age with mean.

```{r}
df <- subset(df,select = -c(PassengerId,Ticket,Name))
df[is.na(df[,"Age"]),"Age"]<-mean(df[,"Age"],na.rm = TRUE)
```

### We used the GBM algorithm, and plotted the model. 
Ploting the model presents all compared configurations with regard to the defined metric.

```{r}
grid <- expand.grid(.n.trees=c(5),.interaction.depth=6,.shrinkage=c(0.1,0.3,0.5),.n.minobsinnode=5)

set.seed(123)
control <- trainControl(method="cv", number=3)
metric <- "Accuracy"
fit.gbm <- train(Survived~., data=df, method="gbm", metric=metric, trControl=control, verbose=FALSE,tuneGrid =grid, na.action = na.pass)
plot(fit.gbm)
```

### Load the test dataframe:

```{r}
new_df <-read.csv('test.csv',na.strings = "")
```

### Save the passengerIds:

```{r}
ids<- new_df$PassengerId
```

### Turn Survived to a factor and delete the same columns we deleted in the train set:

```{r}
new_df$Pclass<- as.factor(new_df$Pclass)
new_df <- subset(new_df,select = -c(PassengerId,Ticket,Name))
```

### After we ran our model, the test data contains some new levels in the *Cabin* feature that did not appear in the train data so we have to add the new levels to the dataframe levels:

```{r}
fit.gbm$xlevels[["Cabin"]] <- union(fit.gbm$xlevels[["Cabin"]], levels(new_df$Cabin))
```

### Predict the rows in the test set with the GBM model:

```{r}
new_pred<- predict(fit.gbm,new_df,na.action = na.pass)
```

### Write the predictions into file:

```{r}
res <- cbind(PassengerId=ids,Survived=as.character(new_pred))
write.csv(res,file="GBM results.csv",row.names = F)

```
